Effects of Sudakov form factor in\\ the Golec-Biernat W\"usthoff saturation model

### 2022-09-21 Document/Effects of Sudakov form factor in the Golec-Biernat Wusthoff model.tex
plots updated

\usepackage[
backend=bibtex,
%style=ieee
maxbibnames=3,
%backend=bibtex,
style=ieee
]{biblatex}
\addbibresource{./ref/golec.bib}
\addbibresource{./ref/gbw1998.bib}
\addbibresource{./ref/bgk2002.bib}
\addbibresource{./ref/impact.bib}
\addbibresource{./ref/cambqcd.bib}
\addbibresource{./ref/gbs2018.bib}
\addbibresource{./ref/gbs2006.bib}
\addbibresource{./ref/xiao2017.bib}
\addbibresource{./ref/minuit.bib}
\addbibresource{./ref/hera.bib}
\addbibresource{./ref/jk2006.bib}
\addbibresource{./ref/FL.bib}
\addbibresource{./ref/stasto2018.bib}
\addbibresource{./ref/stebel2020.bib}
\addbibresource{./ref/ellis1996.bib}
\addbibresource{./ref/bronstein.bib}
\addbibresource{./ref/mueller2016.bib}
\addbibresource{./ref/css1985.bib}
\addbibresource{./ref/prokudin2015.bib}
\addbibresource{./ref/collins2016.bib}

@@

The dipole cross-section $\sigma_{\mathrm{dp}}$ is related to the gluon density and thus contains non-perturbative effects. {\color{blue} Therefore, it has to be, to an extent, modelled. Nonetheless, solving appropriate evolution equeations, such as the Balitsky-Kovchegov equation, is computationally expensive, and thus it is useful to have a simple model to describe the saturation effects.}\\
In the region of large dipole size $r$, multi-gluon exchange becomes important and the saturation effects come into play. The present study has roots in the Golec-Biernat W\"usthoff (GBW) model of the dipole cross-section \cite{gbw1998}, which describes the saturation effects in a very simple form.
In the next section, two models on which we develop our modified versions, namely the Golec-Biernat W\"usthoff (GBW) model\cite{gbw1998} and the Bartels Golec-Biernat Kowalski (BGK) model\cite{bgk2002}, are briefly summarized.  In sections 3 and 4, a summary of the modification is given. In section 5, the result of fitting to the data from the HERA\cite{hera} is presented. %{\color{blue}correction comment in summary}

>>>>

\usepackage[
backend=bibtex,
%style=ieee
maxbibnames=3,
%backend=bibtex,
style=ieee
]{biblatex}
\addbibresource{./ref/golec.bib}
\addbibresource{./ref/gbw1998.bib}
\addbibresource{./ref/bgk2002.bib}
\addbibresource{./ref/impact.bib}
\addbibresource{./ref/cambqcd.bib}
\addbibresource{./ref/gbs2018.bib}
\addbibresource{./ref/gbs2006.bib}
\addbibresource{./ref/xiao2017.bib}
\addbibresource{./ref/minuit.bib}
\addbibresource{./ref/hera.bib}
\addbibresource{./ref/jk2006.bib}
\addbibresource{./ref/FL.bib}
\addbibresource{./ref/kutak2005.bib}
\addbibresource{./ref/stasto2018.bib}
\addbibresource{./ref/stebel2020.bib}
\addbibresource{./ref/ellis1996.bib}
\addbibresource{./ref/bronstein.bib}
\addbibresource{./ref/mueller2016.bib}
\addbibresource{./ref/css1985.bib}
\addbibresource{./ref/prokudin2015.bib}
\addbibresource{./ref/collins2016.bib}

@@

The dipole cross-section $\sigma_{\mathrm{dp}}$ is related to the gluon density and thus contains non-perturbative effects. {\color{blue} Therefore, it has to be, to an extent, modelled. Nonetheless, solving appropriate evolution equeations, such as the Balitsky-Kovchegov (BK) equation, is computationally expensive, and thus it is useful to have a simple model to describe the saturation effects. (see Ref.~\cite{kutak2005} for the comparison of a solution of the BK equation and the model we will discuss in the next section.)}\\
In the region of large dipole size $r$, multi-gluon exchange becomes important and the saturation effects come into play. The present study has roots in the Golec-Biernat W\"usthoff (GBW) model of the dipole cross-section \cite{gbw1998}, which describes the saturation effects in a very simple form.
In the next section, two models on which we develop our modified versions, namely the Golec-Biernat W\"usthoff (GBW) model\cite{gbw1998} and the Bartels Golec-Biernat Kowalski (BGK) model\cite{bgk2002}, are briefly summarized.  In sections 3 and 4, a summary of the modification is given. In section 5, the result of fitting to the data from the HERA\cite{hera} is presented. %{\color{blue}correction comment in summary}
